```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, fig.show = 'hold', fig.cap = "")
```

\blandscape
::: {fig-cr-s3}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Convergence Rate and Rate of Proper Solutions in Study 3\\label{fig:convergence-study-3}"}
fig_conv_rate_study3
```

::: {fig-note}
\raggedright \textit{Note.} Convergence and proper solutions (in parentheses) rates across sample sizes (*N*), reliability (*r*), and model misspecifications for global SAM (gSAM), local SAM with maximum likelihood (lSAM-ML), unweighted least squares (lSAM-ULS), and SEM. Graphic adapted from @dhaene_evaluation_2023.
:::
:::

::: {fig-rmse-aggregated-study1}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Mean Average Root Mean Squared Error (RMSE) of Regression Parameters in Study 1\\label{fig:rmse-aggregated-study1}"}
print(fig_rmse_aggregated_study1)
```

:::{fig-note}
\fontsize{10}{12}\selectfont
\raggedright \textit{Note.} Mean RMSE averaged (in absolute values) over all parameters in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with maximum likelihood (lSAM-ML), unweighted least squares (lSAM-ULS) and SEM. Monte Carlo standard error (MCSE) in parentheses. Graphic adapted from @dhaene_evaluation_2023.
:::
:::

::: {fig-cr-study2}
```{r fig.width=12, fig.height=5.5, fig.cap="Convergence Rate and Rate of Proper Solutions in Study 2\\label{fig:convergence-study-2}"}
print(p_convergence_heatmap_study2)
```

:::{fig-note}
\fontsize{10}{12}\selectfont
\raggedright \textit{Note.} Convergence and proper solutions (in parentheses) rates across sample sizes (N), reliability (r), and model misspecification location for global SAM (gSAM), local SAM with maximum likelihood (lSAM-ML), unweighted least squares (lSAM-ULS), and SEM. Graphic adapted from @dhaene_evaluation_2023.
:::
:::

::: {fig-relbias-aggregated-study2}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Relative Bias of Regression Parameters in Study 2\\label{fig:relbias-aggregated-study2}"}
print(fig_relbias_aggregated_study2)
```

:::{fig-note}
\fontsize{10}{12}\selectfont
\raggedright \textit{Note.} Mean relative bias averaged (in absolute values) over all parameters in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with maximum likelihood (lSAM-ML), unweighted least squares (lSAM-ULS) and SEM. * indicating Monte Carlo standard error (MCSE) above 10% of the estimate. Graphic adapted from @dhaene_evaluation_2023.
:::
:::

::: {fig-relrmse-aggregated-study2}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Relative RMSE of Regression Parameters in Study 2\\label{fig:relrmse-aggregated-study2}"}
print(fig_relrmse_aggregated_study2)
```

:::{fig-note}
\fontsize{10}{12}\selectfont
\raggedright \textit{Note.} Mean relative RMSE averaged (in absolute values) over all parameters in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with maximum likelihood (lSAM-ML), unweighted least squares (lSAM-ULS) and SEM. * indicating Monte Carlo standard error (MCSE) above 10% of the estimate. Graphic adapted from @dhaene_evaluation_2023.
:::
:::

::: {fig-bias-misspecified-study2}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Bias of Misspecified Regression Parameters in Study 2\\label{fig:bias-misspecified-study2}"}
print(fig_bias_aggregated_misspec_study2)
```

:::{fig-note}
\fontsize{10}{12}\selectfont
\raggedright \textit{Note.} Mean bias of parameters absent in the population and misspecified in the analysis model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with maximum likelihood (lSAM-ML), unweighted least squares (lSAM-ULS) and SEM. * indicating Monte Carlo standard error (MCSE) above 10% of the estimate. Graphic adapted from @dhaene_evaluation_2023.
:::
:::
\elandscape