```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, fig.show = 'hold', fig.cap = "")
```

\blandscape
::: {fig-cr-study2}
```{r fig.width=12, fig.height=5.5, fig.cap="Convergence Rate and Rate of Proper Solutions in Study 2\\label{fig:convergence-study-2}"}
print(p_convergence_heatmap_study2)
```

:::{fig-note}
\raggedright \textit{Note.} Convergence and proper solutions (in parentheses) rates across sample sizes (N), reliability (r), and model misspecification location for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS), and SEM.
:::
:::

::: {fig-rmse-aggregated-study1}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Mean Average Root Mean Squared Error (RMSE) of Regression Parameters in Study 1\\label{fig:rmse-aggregated-study1}"}
print(fig_rmse_aggregated_study1)
```

:::{fig-note}
\raggedright \textit{Note.} Mean RMSE averaged (in absolute values) over all parameters in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM.
:::
:::

::: {fig-relbias-aggregated-study2}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Relative Bias of Regression Parameters in Study 2\\label{fig:relbias-aggregated-study2}"}
print(fig_relbias_aggregated_study2)
```

:::{fig-note}
\raggedright \textit{Note.} Mean relative bias averaged (in absolute values) over all parameters in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM.
:::
:::

::: {fig-relrmse-aggregated-study2}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Relative RMSE of Regression Parameters in Study 2\\label{fig:relrmse-aggregated-study2}"}
print(fig_relrmse_aggregated_study2)
```

:::{fig-note}
\raggedright \textit{Note.} Mean relative RMSE averaged (in absolute values) over all parameters in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM.
:::
:::

::: {fig-bias-misspecified-study2}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Relative Bias of Misspecified Regression Parameters in Study 2\\label{fig:bias-misspecified-study2}"}
print(fig_bias_misspecified_study2)
```

:::{fig-note}
\raggedright \textit{Note.} Mean relative bias of parameters absent in the population and misspecified in the analysis model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM.
:::
:::

::: {fig-rmse-parameterwise-study3}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Mean RMSE of Regression Parameters in Study 3\\label{fig:rmse-parameterwise-study3}"}
print(fig_rmse_parameterwise_study3)
```

:::{fig-note}
\raggedright \textit{Note.} Mean absolute RMSE for each parameter with true value of 0.1 in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM.
:::
:::

::: {fig-bias-aggregated-study3}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Mean Bias of Regression Parameters in Study 3\\label{fig:bias-aggregated-study3}"}
```

:::{fig-note}
\raggedright \textit{Note.} Mean absolute bias averaged (in absolute values) over all parameters in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM.
:::
:::

::: {fig-rmse-aggregated-study3}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Mean RMSE of Regression Parameters in Study 3\\label{fig:rmse-aggregated-study3}"}
print(fig_rmse_aggregated_study3)
```

:::{fig-note}
\raggedright \textit{Note.} Mean RMSE averaged (in absolute values) over all parameters in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM.
:::
:::
\elandscape