\setlength{\parindent}{1.27cm}
```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

The joint study showed that using bound maximum likelihood estimation for standard SEM as proposed by Kosanke did infact eliminate the convergence issues convergence rate as well as improper solutions issues in all conditions. Next a parameterwise comparison of the bias of the path coeffecient estimates averaged across each model in absolute values showed... (see Figure \ref{fig:bias-parameterwise-study3}). The RMSE of the path coeffecients showd a similar pattern as the bias with... (see Figurefig:rmse-parameterwise-study3). Aggregating the metrics across all parameters in one model showed that... (see Figure \ref{fig:bias-aggregated-study3} and Figure \ref{fig:rmse-aggregated-study3}).

There was little to no difference between gSAM and lSAM with lSAM being very slightly less biased in most conditions.

\blandscape
::: {fig-cr-s3}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Convergence Rate and Rate of Proper Solutions in Study 3\\label{fig:convergence-study-3}"}
fig_conv_rate_study3
```

::: {fig-note}
\raggedright \textit{Note.} Convergence and proper solutions (in parentheses) rates across sample sizes (*N*), reliability (*r*), and model misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS), and SEM.
:::
:::

::: {fig-bias-parameterwise-study3}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Mean Bias of Regression Parameters in *Joint* Study\\label{fig:bias-parameterwise-study3}"}
fig_bias_parameterwise_study3
```

:::{fig-note}
\raggedright \textit{Note.} Mean absolute bias for each parameter with true value of 0.1 in one model for sample sizes (*N*), reliability (*r*), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM.
:::
:::


::: {fig-sam-sem-diff-study3}
```{r, echo=FALSE, fig.width=12, fig.height=6.5, fig.cap="Aggregated Mean Difference between Bound Standard SEM and SAM Estimation in Bias and RMSE of regression coefficients estimates in *Joint* Study\\label{fig:sam-sem-diff-study3}"}
fig_sam_sem_diff_study3
```

:::{fig-note}

\raggedright \textit{Note.} Bias (top) and RMSE (bottom) differences between SEM and gloabal and local SAM (gSAM and lSAM) , averaged across estimates of true regression coefficients (0.1) over varying *N*, *r*, and misspecifications. Error bars show Monte Carlo SEs.
:::
:::

::: {fig-bias-aggregated-study3}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Aggregated Mean Bias of Regression Parameter Estimates in *Joint* Study \\label{fig:bias-aggregated-study3}"}
fig_bias_aggregated_study3
```

:::{fig-note}
\raggedright \textit{Note.} Mean bias of regression parameters avereaged across all estimates of each condition for sample sizes (*N*), reliability (*r*), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML) and SEM (bound and unbound ML).
:::
:::
\elandscape
