\setlength{\parindent}{1.27cm}
```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

There were no convergence issues for all SAM methods (gSAM, lSAM ML and ULS) with a convergence rate of 100% and no improper solutions across all conditions even in small samples with low reliability. Standard SEM however showed severe convergence issues in small samples with low to moderate reliability with a convergence rate of as low as 50% and 50% improper solutions in the cross loading misspecification condition as the most challenging condition (see Figure \ref{fig:convergence-study-1}). Convergence rates in study 2 were consistent with this with 100% convergence rates for all SAM methods and as low as 60% for standard SEM with exogenous measurement misspecifications posing more challenges than endogenous misspecifications (see Figure \ref{fig:convergence-study-2} in Appendix B).

Next the bias of the path coeffecient estimates averaged across each model in absolute values showed that all SAM methods were more accurate than standard SEM especially under omitted cross loadings in the analysis model (See Figure 6).


\blandscape
::: {fig-cr-s1}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Convergence Rate and Rate of Proper Solutions in Study 1\\label{fig:convergence-study-1}"}
print(fig_conv_rate_study1)
```

::: {fig-note}
\raggedright \textit{Note.} Convergence and proper solutions (in parentheses) rates across sample sizes (N), reliability (r), and model misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS), and SEM.
:::
:::

::: {fig-bias-aggregated-study1}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Mean Average Bias of Regression Parameters in Study 1"}
print(fig_bias_aggregated_study1)
```

:::{fig-note}
\raggedright \textit{Note.} Mean absolute bias averaged (in absolute values) over all parameters with true value of 0.1 in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM. Monte Carlos Standard Errors (MCSE) are shown in parentheses for each value.
:::
:::
\elandscape

