\setlength{\parindent}{1.27cm}
```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

The joint study showed that using bound maximum likelihood estimation for standard SEM as proposed by Collaborator B did, in fact, eliminate the low convergence rate as well as improper solutions in all conditions (see \ref{fig:convergence-study-3}). Next, the parameter-wise signed mean bias values of the single regression weight estimates showed that omitting positive cross-loadings results in an overall positive bias, whereas omitting negative cross-loadings results in a negative bias. As in previous studies, the positive bias was less pronounced for SAM (gSAM and lSAM) than for SEM, especially with lower sample sizes and reliability. However, contrary to the findings by Collaborator B and Robitzsch (2022), in this study, the negative bias was also less pronounced for both SAM methods. Conditions with omitted correlated residual correlations resulted in predominantly negative bias values for all methods irrespective of the sign of the misspecification, with standard SEM being slightly less biased than SAM methods (see Figure \ref{fig:bias-parameter-wise-study3}).
A direct comparison of standard SEM with SAM for bias and RMSE showed that SAM methods were less biased for cross-loadings and, when accounting for variance via RMSE, more accurate, especially in smaller sample sizes and indicator reliability levels (see Figure \ref{fig:sam-sem-diff-study3}). Further, there were little to no differences between gSAM and lSAM, with lSAM being slightly more accurate overall in terms of RMSE.
Overall these findings suggest that the explanation for SAM's lower bias under positive misspecifications being due to a general negative bias that would lead to overly negative bias in case of negative measurement misspecifications (proposed by Collaborator B and @robitzsch_comparing_2022) does not hold in a more complex (and realistic) model that SAM could be favorable choice of SEM estimation especially challenging conditions.

\blandscape
::: {fig-bias-parameter-wise-study3}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Mean Bias of Regression Parameters in *Joint* Study\\label{fig:bias-parameter-wise-study3}"}
fig_bias_parameterwise_study3
```

:::{fig-note}
\raggedright \textit{Note.} Mean absolute bias for each parameter with a true value of 0.1 in one model for sample sizes (*N*), reliability (*r*), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM. Grey fields indicate excluded conditions with convergence rate below 50%.
:::
:::

::: {fig-sam-sem-diff-study3}
```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Aggregated Mean Difference between Bound Standard SEM and SAM Estimation in Bias and RMSE of regression coefficients estimates in *Joint* Study\\label{fig:sam-sem-diff-study3}"}
fig_sam_sem_diff_study3
```

:::{fig-note}

\raggedright \textit{Note.} bias (top) and RMSE (bottom) differences between SEM and global and local SAM (gSAM and lSAM), averaged across estimates of true regression coefficients (0.1) over varying sample size (*N*), reliability (*r*), and misspecifications. Error bars indicate Monte Carlo Standard Errors.
:::
:::
\elandscape
