\setlength{\parindent}{1.27cm}
```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

There were no convergence issues for all SAM methods (gSAM, lSAM ML, and ULS) with a convergence rate of 100% and no improper solutions across all conditions, even in small samples with low reliability. Standard SEM demonstrated severe convergence issues, particularly in small samples with low to moderate reliability. The convergence rate was as low as 50%, with 50% of the solutions being improper, especially under the challenging condition of cross-loading misspecification (see Figure \ref{fig:convergence-study-1}).
Next, the bias of the path coefficient estimates averaged across each model in absolute values showed that in small to medium sample sizes with low to moderate reliability, SAM methods were mostly closer to the true parameters than standard SEM. This difference was especially pronounced under omitted cross-loadings in the analysis model. However under correlated residuals standard SEM was slightly less biased.
Large sample sizes and high reliability conditions showed the least bias overall, with no differences observed between the methods (see Figure \ref{fig:bias-aggregated-study1}). Further, among the different SAM methods, there was no difference between gSAM and lSAM-ML, while lSAM-ULS performed slightly worse. This pattern was mostly consistent with the RMSE of the path coefficients: SAM methods showed lower values than standard SEM in small to medium sample sizes with low to moderate reliability, indicating higher overall accuracy for SAM methods in challenging conditions. This was notably also the case under correlated residuals where SEM was less biased, which highlights SAM’s advantage here as well in light of a trade-off between (slightly higher) bias and precision (see Figure \ref{fig:rmse-aggregated-study1}). In contrast to the bias, the RMSE showed that lSAM-ML performed better than gSAM and lSAM-ULS under cross-loading and structural misspecifications. However, SAM methods, even though outperforming standard SEM under omitted cross-loadings, still showed substantial deviations in this condition (with bias values between 69% and 77% of the true value for SAM-ML) and inaccuracy (with RMSE values between 86% and 277% of the true value for SAM-ML). Additionally, while increased sample size led to lower RMSE values for all methods, bias only decreased for standard SEM in larger samples. In contrast, SAM methods showed a slight increase in bias with larger samples with measurement misspecifications in low and moderate reliability.


\blandscape
::: {fig-cr-s1}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Convergence Rate and Rate of Proper Solutions in Study 1\\label{fig:convergence-study-1}"}
print(fig_conv_rate_study1)
```

::: {fig-note}
\raggedright \textit{Note.} Convergence and proper solutions (in parentheses) rates across sample sizes (N), reliability (r), and model misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS), and SEM.
:::
:::

::: {fig-bias-aggregated-study1}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Mean Average Bias of Regression Parameters in Study 1\\label{fig:bias-aggregated-study1}"}
print(fig_bias_aggregated_study1)
```

:::{fig-note}
\raggedright \textit{Note.} Mean absolute bias averaged (in absolute values) over all parameters with true value of 0.1 in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM. Monte Carlos Standard Errors (MCSE) are shown in parentheses for each value.
:::
:::
\elandscape

The pattern of results from study 1 was consistent with the findings of study 2, with some additional insights regarding the study-specific conditions. Firstly, as in study 1, there was a 100% convergence rate and rate of proper solutions for all SAM methods across all conditions, even in small samples with low reliability. Standard SEM, in contrast, showed severe convergence issues and frequent improper solutions in small samples with low reliability, with exogenous misspecifications being more challenging than endogenous misspecifications (see Figure \ref{fig:convergence-study-2}).

Further, in study 2 the relative bias (to account for modulated path coefficients) of the correctly specified path coefficient estimates averaged across each model in absolute values showed again that in small to medium sample sizes with low to moderate reliability, all SAM estimations were closer to the true parameters than standard SEM. This increased performance of SAM was present only for gSAM and lSAM across all item reliability levels with separate measurement blocks for each factor (b = 5), indicating that joining measurement models in lSAM for exo- and endogenous factors (b = 3) was disadvantageous. All methods performed worse for lower variance explained by the structural model in low and moderate reliability and measurement missepcifcations except SAM methods (with b = 5 and gSAM). The average relative RMSE values of the path coefficients paint a similar picture. Here, too, lower $R^2$ values were more challenging. Other than for the bias, exogenous misspecifications were more challenging than endogenous misspecifications. Further, gSAM and lSAM-ML with five measurement blocks (here not ULS) produced notably lower RMSE values than standard SEM; however, only in small and medium samples with low item reliability present.
As all population models included structural misspecifications in study 2, there was also a slight advantage visible in low sample size and low reliability without measurement misspecification, indicating that SAM methods are also more robust to the impact of falsely specified paths not present in the population on the estimation of the remaining correctly specified parameters.
Figure \ref{fig:bias-misspecified-study2} shows the absolute bias of the parameters misspecified (excluded from the results presented above to avoid distortion of relative metric values by parameters with a true value of 0), indicating that also such parameters are recovered more accurately by SAM methods than standard SEM but only if measurement misspecifications are present.

\blandscape
::: {fig-relbias-aggregated-study2}
```{r, echo=FALSE, fig.width=12, fig.height=5.5, fig.cap="Mean Average Relative Bias of Regression Parameters in Study 2\\label{fig:relbias-aggregated-study2}"}
print(fig_relbias_aggregated_study2)
```

:::{fig-note}
\raggedright \textit{Note.} Mean relative bias averaged (in absolute values) over all parameters in one model for sample sizes (N), reliability (r), and misspecifications for global SAM (gSAM), local SAM with Maximum Likelihood (lSAM-ML), Unweighted Least Squares (lSAM-ULS) and SEM.
:::
:::
\elandscape

Overall, the results indicate that SAM methods (gSAM, lSAM-ML, and lSAM-ULS) outperformed standard SEM under challenging conditions. SAM methods achieved a 100% convergence rate with no improper solutions, even in small samples with low reliability, whereas standard SEM exhibited severe convergence issues and high rates of improper solutions, particularly with cross-loading misspecification. SAM methods provided less biased and more accurate path coefficient estimates, especially in small to medium samples with low to moderate reliability and measurement misspecifications like omitted cross-loadings. Among the SAM variants, gSAM and lSAM-ML generally performed better than lSAM-ULS, with lSAM-ML showing superior accuracy under cross-loading and structural misspecifications. Further, separate compared to joint measurement models in lSAM for latent variables was advantageous. Additionally, SAM methods in Study 2 were more robust to structural misspecifications, providing more accurate estimates of correctly specified parameters even when incorrect paths were included in the model.