---
Title: "Thesis"
author: "Valentin Kriegmair"
fig-cap-location: top
format:
    pdf:
        fontsize: 12pt
        linestretch: 1.5
        geometry: "left=25mm, right=20mm, top=20mm, bottom=20mm"
        classoption: oneside
        papersize: a4
        header-includes:
           - \usepackage{float}
           - \floatplacement{table}{H}
           - \usepackage{tikz}
           - \usetikzlibrary{arrows.meta, positioning, calc}
           - \usepackage{geometry}
           - \geometry{margin=1in}
           - \usepackage{caption}
           - \captionsetup{justification=raggedright, singlelinecheck=false, parskip=0pt}



fontsize: 12pt
engine: knitr
bibliography: ../bibliography.bib
csl: ../apa.csl
---
```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```


# Introduction

# Methods

## A Framework for Adversarial Collaboration

## Methods of Individual Simulation Studies

### Studies by Kriegmair

{{< include methods.qmd >}}

### Studies by Kosanke

```{r, results = 'asis'}
# # Read original methods section from Kosanke
# lines <- readLines("../../LK/thesis.qmd")

# # Find the indices of "### Methods" and "### Results" headings
# methods_headings <- grep("^### Methods", lines)
# results_headings <- grep("^### Results", lines)

# # Extract content between the second occurrence of Methods and Results
# start <- methods_headings[2]
# end <- results_headings[2]
# extracted_lines <- lines[(start):(end-1)]

# # Detect the placeholder for the table (e.g., "**Table 7**")
# table_placeholder <- grep("\\*\\*Table 7\\*\\*", extracted_lines)

# # Split content into before and after the table placeholder
# before_table <- extracted_lines[1:(table_placeholder - 1)]
# after_table <- extracted_lines[(table_placeholder + 1):length(extracted_lines)]

# # Filter out any unwanted lines, including "Overview of the individual simulation studies by Leonard Kosanke"
# before_table <- before_table[!grepl("Overview of the individual simulation studies by Leonard Kosanke.", before_table)]
# before_table <- before_table[!grepl("\\*\\*Table 7\\*\\*", before_table)]  # Filter out "**Table 7**"

# # Output the content before the table
# cat(paste(before_table, collapse = "\n"))
```


:::{fig-kosanke-studies}

```{r schematic_1, echo=FALSE, out.width="125%"}
# knitr::include_graphics("../../LK/images/TableOverviewIndividualStudies.pdf")
```

\raggedright \textit{Note.} $\Phi$: factor correlation, N: sample size, $\lambda$: factor loading, $\sigma$: residual variance, $\tau$: factor variance, RC: residual correlations, CL: cross-loadings, CFA: confirmatory factor analysis, $\beta$: regression coefficient between factors.

Overview of Simulation Studies conducted by Kosanke

:::

```{r, results = 'asis'}
# # Filter out the unwanted raw code and remaining unwanted lines after the table
# after_table <- after_table[!grepl("\\{r|knitr::include_graphics|```", after_table)]
# after_table <- after_table[!grepl("Overview of the individual simulation studies by Leonard Kosanke.", after_table)]

# # Output the content after the table
# cat(paste(after_table, collapse = "\n"))
```

## Methods of "Joint" Simulation Study

{{< include methods_joint.qmd >}}

# Results

## Results of Individual Simulation Studies

### Results of Kriegmair's Simulation Studies

{{< include results_all.qmd >}}

### Results of Kosanke's Simulation Studies

## Results of the "Joint" Simulation Study

## Results of the Adversarial Collaboration

# Discussion

## Discussing the substanital results

## Disucssing the Adversarial Collaboration

Idea: living simulations