---
title: "Adversarial Simulation"
subtitle: "A case study"
author: "Leonard Kosanke"
format:
    pdf:
        fontsize: 12pt
        linestretch: 1.5
        geometry: "left=25mm, right=20mm, top=20mm, bottom=20mm"
        classoption: oneside
        papersize: a4
        header-includes:
           - \usepackage{float}
           - \floatplacement{table}{H}
fontsize: 12pt
bibliography: ../bibliography.bib
engine: knitr
---

The git hash is: `{r} suppressWarnings(system2("git", c("rev-parse", "--short=5", "HEAD"), stdout = TRUE, stderr = TRUE))`

```{r}
library(here)
library(knitr)
```

# Introduction

Monte Carlo simulations are an extensively utilized tool for assessing and comparing statistical methods in quantitative empirical science. 
They are used to evaluate the performance of estimation and inference methods by analyzing them in light of known simulated population models and values.
Despite the clear insight into the underlying data structures that simulations provide, they are not immune to common pitfalls that thus far have been predominantly associated with the replication crisis in empirical research [@lohmann_its_2022].
In simulation studies, a key challenge is ensuring that results can be generalized to real-world applications.
These studies must ensure that the chosen performance metrics, experimental factors, and inference models accurately reflect and test real-world scenarios. 
Given the impracticality of simulating every possible model, method and use case, these studies inherently involve a multitude of decision-making elements potentially prone to bias. 
For example, the decisions of selecting evaluation criteria for competing methods (for example absolute versus relative bias of performance), selecting which models or methods to compare in the first place, and which simulation specifications to run (for example deciding on which sample size to simulate), can have substantive impact on the results.
Evidently, many issues of open science in the empirical realm are present in the context of simulation studies as well. 
One approach that addresses these issues at the level of value selection suggests to sample all relevant values from existing results published in the empirical literature of interest [@bollmann_what_2015]. 
An example application could be to decide on a simulated sample size not just based on a hunch or prior experience, but based on previous empirical studies conducted in the field. 
Even though this idea is fruitful and improves upon the problem of generalizability, the argument with regards to the arbitrariness of decision-making still remains. 
For example, deciding on which papers, or even which models within a paper to select (and which not), can still be subject to individual bias or simply chance. 
Additionally, conducting extensive literature reviews for all parameter values chosen is very time-consuming and difficult to apply in practice.

Another approach to tackle these challenges that has been proposed in the empirical context is Adversarial Collaboration (AC). 
Adversarial collaboration, piloted by @mellers_frequency_2001 and popularized by @kahneman_thinking_2011, is a research method increasingly recognized within the quantitative empirical research community for enhancing scientific rigor. 
Praised as “The next science reform” adversarial collaboration is the process of disagreeing scholars working jointly to resolve scientific disputes [@clark_adversarial_2021]. 
An ongoing effort by @melloni_adversarial_2023, for example, conducts Adversarial Collaboration between proponents of two different theories on the relationship between consciousness and brain activity, hoping to advance research in this field. 
Adversarial Collaboration entails identifying points of empirical disagreement, designing mutually agreed upon studies to test competing hypotheses, and jointly publishing results, irrespective of the outcome. 
The idea is that in conducting adversarial collaboration, fair comparison and truthful representation of opposing views can be achieved, thereby enhancing epistemic accountability and reducing research ambiguity in scientific decision-making. 
Additionally, juxtaposing and debating competing positions in this way can improve generalizability of results.

Our goal is to transfer the benefits of adversarial collaboration to simulation studies. 
To do so, we conducted a focused case study, utilizing an exemplary topic in the literature of simulation studies: comparing a newly proposed iterative structural after measurement (SAM) estimation approach to structural equation model (SEM) estimation with traditional, non-iterative SEM estimation [@dhaene_evaluation_2023; @robitzsch_comparing_2022; @rosseel_structural_2022]. 
In their respective simulations, the authors' results differed up to the point of contradiction, providing us with ideal grounds for conducting adversarial collaboration. 
While @dhaene_evaluation_2023 concluded that SAM estimation generally outperforms non-iterative SEM in small samples, @robitzsch_comparing_2022 did not find the methods to differ. 
Similarly, whereas the former found SAM to be more robust against model misspecification, the latter argued the opposite to be true. 
Applying Adversarial Collaboration, we, the authors of this paper, each represented one of these competing positions, as detailed later.

This allows us to examine the practical feasibility of adversarial collaboration in Monte Carlo simulation studies as well its potential to enhance methodological rigor and generalizability in this domain of research. 
Thus, this investigation leads us to address the following research question:

Can adversarial collaboration be applied to simulation studies, in terms of practical applicability and technical feasibility?

# Methods 

This section contains two parts. 
First, an outline of the AC framework we agreed upon before the start of the collaboration.
Then, each sides describes the methods they used to answer the substantive research question of the individual studies.
To answer this research question, we created and followed the following procedure for the adversarial collaboration process: 

## Outline of the Adversarial Collaboration

The procedure consists of two parts. In the first part, each researcher conducts an independent preliminary study as a replication of their side of the argument. 
Leonard Kosanke replicated relevant parts of the study by @robitzsch_comparing_2022, and Valentin Kriegmair replicated the study by @dhaene_evaluation_2023. 
The replications included the generation of individual simulation protocols, as suggested by @morris_using_2019. 
These can be accessed in our Github-repository, under releases: <https://github.com/lkosanke/AdversarialSimulation/tree/main/>.
In the second part, a joint study, including a joint simulation protocol, was pursued. 
Here, the main part of the adversarial collaboration took place. 
Each step of the individual simulation studies (from the substantive research question up until the interpretation of the results) was scrutinized and debated between collaborators, using adversarial collaboration techniques.
Decisions were made and documented based on the most convincing argument presented, if possible. 
This process started based on the results of Part 1.
To facilitate a structured comparison and integration of our studies through the collaboration process, we agreed on a framework for conducting our individual simulation studies in advance, that is visible in Table 1.  

Table 1: Structure of simulation studies 
1. Defining aims and objectives / Research Question of Interest. ( = verbal description) 
o as specific as possible 
o e.g. examination of goodness-of-fit statistics under varying degrees of 
misspecification 
o comparison of the maximum likelihood (ML) to (2SLS) 
2. Specification of Population Model 
o Optional and depending on field of simulation 
Modularities: 
o Structure: (e.g. CFA or SEM) 
o Size: number of latents and indicators 
o Complexity: (cross-loaded indicators, Reciprocal paths, Exogenous 
predictors) 
→ select target model for (assumed) general model types 
3. Data Generation Mechanism 
o resampling vs. parametric model draw 
o random number draw for data generation 
4. Experimental Design Simulation Procedures 
o Determine what factors to vary, on what levels, and whether fully, or partly 
factorially or one at a time (factor = scenario in Morris et al., 2019) 
o e.g. 
▪ sample size 
▪ distribution of the observed variables 
▪ extent of misspecification 
… 
5. Method Selection 
o Varies depending on research question 
o e.g. 
▪ type of and number of estimation methods to be compared 
6. Defining Estimands / Population level values 
o should reflect values commonly encountered in applied research. 
o e.g. 
▪ R2 values the chosen coefficients produce should also be reasonable 
for applied research. 
▪ parameters of the model should be statistically significant, even at the 
smallest sample size of the simulation. 
▪ consider power issues (e.g.:enough power to detect misspecification, 
too much power to detect misspecification at all sample sizes?) 
▪ “bias” in the estimates that will be introduced by the misspecification. 
7. Performance Measures 
o Selection and justification of use of e.g. 
▪ Bias 
▪ sensitivity/ specificity 
▪ predictive accuracy 
o decision on number of simulations for acceptable Monte Carlo SE for these 
measures 
8. Software Selection 
o to run simulation 
o packages & functions 
9. Analysis and Interpretation plan 
o Analysis: descriptive vs. inferential 
o Interpretation: decision criteria that evaluate performance : e.g. if 1-ß > 90, 
the method performs well 

Before Coding and Execution: Anticipating all critical decision processes (e.g. exclusion 
criteria for “imperfect” samples) 
10. Coding and Execution 
o Amount and content of scripts 
o include (sanity) checks 
o setting seeds 
o troubleshooting & verification 
11. Analyzing results 
o descriptive 
o graphical 
o inferential 
o exploration 
12. Reporting & Presentation 
o provide rationales for each choice made in the previous steps 
o publishing code and simulated data 

End of Table 1 

This framework allows for the expected divergences in results of the individual simulations, and at the same time provides a basis for systematic comparison and synthesis for the joint simulation. 
Additionally, we have identified two substantive research questions to co-align the individual simulation studies: 

1. How do SAM and traditional SEM methods (including ML and ULS) compare in terms of bias, Mean Squared Error (MSE), and convergence rates in small to moderate samples? 

2. What is the impact of model misspecifications, such as residual correlations and cross-loadings, on the performance of SAM compared to traditional SEM methods? 

In the end, each collaborator reports the results in their own paper. 
We are aware that adversarial collaboration has its limitations when it comes to decision making in joint studies, and has lead to unresolvable disagreements in previous studies [@cowan_how_2020; @mellers_frequency_2001). 
In order to mitigate this risk, we conducted the joint study in a structured and formalized manner. 
To this end, we used the tools presented in Table 2. 
These were also meant to facilitate the evaluation of the adversarial collaboration with regards to our main research question. 

 

Table 2: Adversarial Collaboration (AC) Techniques: 

At each step of decision making in the Joint Study, any of the following techniques 


Thesis of: Leonard Kosanke 

can be used, depending on their applicability: 

 

• Core Disagreements: Arrive at clearly defined core disagreements that might be the origin 
for conflicts. (Clark et al., 2022) 

 

• Assumption check: List, question, and categorize assumptions (Kardos Dexter, 2017) 

 

• Red-Teaming: Generating what if scenarios, to identify limitations of the adversaries’ 
approach (Kardos Dexter, 2017) 

 

• Quality of information (Kardos Dexter, 2017): checking the adversaries’ quality of 
evidence based on literature. 

 

• Third neutral arbiter: In case of fundamentally unresolvable disagreements, a third 
neutral arbiter (Aaron Peikert) will be consulted to try to resolve them. 

 

End of table 2 


### Documentation - Decision log 

As the number of decisions made and their documentation is large, only the most important results are presented in this paper. 
In addition, the appendix contains a separate decision log with a detailed and complete documentation of all decisions made. 
Here, we summarized the results of the AC-techniques used for each step of the simulation study, as well as their consequence for the decision-making process. 
Another aspect of structuring the collaboration, within the decision log, lied in the way we tackle decision making in the joint study. 
In our mind, decision making can be based on four distinct grounds: Evidence-based, pragmatic reasons, arbitrary reasons or other reasons (e.g. personal values, political issues). 
Firstly, we deem a decision evidence based, if we can find a clear answer for a disagreement, based on empirical evidence or in the literature more general. 
Secondly, to be able to keep the scope of this project, we can argue and make decisions for pragmatic reasons, as for example time needed to implement another condition that could be added. 
Thirdly, arbitrary reasons could be any agreement where the first too grounds are not present, but still a decision has to be made. 
Importantly, while this reason does not help in deciding for an option directly, it helps in understanding how often there is no substantive or pragmatic reason for decisions in simulation studies.
If this is the case, we might resort deciding at random. Lastly, there might be other reasons that lead to a decision, that we do not anticipate as of now or did not deem to be likely enough to get their own category for our purpose.  
These four reasons grounded our decision making. 
In some cases, more than one of these reasons were present. 
In such cases, we ranked their relevance to a decision, if possible. An example is the log entry in figure 1: 


Figure 1: Exemplary log entry for deciding for a range of sample sizes 

 

Decision element: factor of sample sizes 

 

Result: c(50, 100, 200) 


 

Grounds: Primary - Evidence-based, as per Peikert et al. (2020); 

 

Secondary – pragmatic reason, based on the average of individual suggestions. 

 

Evaluation - Diary entries 

 

End of figure 1 

### Diary

We documented and evaluated the adversarial collaboration in Part 2 (Joint study) from 
each collaborators subjective perspective using semi-structured diary entries based on @shah_exploring_2016, after each step. 
This had two purposes: Firstly, accumulating evidence for the evaluation of the AC and the collaboration procedure we propose. Secondly, we wanted to capture information that can help us improve this procedure. 
Thus, the resulting diaries were used to evaluate the applicability of the adversarial collaboration and answer the research question. 
The evaluation of the diary entry was conducted in a semi-structured and comparative manner, resorting for example to analysis of quantity of words. 

## Methods for Replicating Robitzsch (2022)

The structure of this section closely aligns to our agreed upon structure of simulation studies.

In a first step, I published a simulation protocol containing all the planned analysis to be replicated from the original paper by @robitzsch_comparing_2022.
This protocol can be accessed here: <https://github.com/lkosanke/AdversarialSimulation/blob/main/LK/simulation_protocol.pdf>.

**Aims, objectives and research questions**
For my individual study, I replicated parts of @robitzsch_comparing_2022 that were relevant to our substantive research questions:

1. How do SAM and traditional SEM methods (including ML and ULS) compare in terms of bias, Mean Squared Error (MSE), and convergence rates in small to moderate samples? 

2. What is the impact of model misspecifications, such as residual correlations and cross-loadings, on the performance of SAM compared to traditional SEM methods? 

Overall, I conducted 6 simulation studies.

**Population Models and Data Generation Mechanisms**

The most important details with regards to the population models and data-generating mechanisms are visible in Table 1.

```{r schematic 1, eval = TRUE, echo = FALSE, out.width="110%"}

knitr::include_graphics(here::here("LK/images/TableOverviewIndividualStudies.pdf"))

```

With regards to the population models, all factors in all studies loaded onto 3 indicators each.
I chose the population values to align to the original paper by @robitzsch_comparing_2022.
For more details on the exact values of each study, see the simulation scripts in the github repository.
The multivariate normally distributed data was generated parametrically, based on a specified population model.
All simulations were conducted using seeds to allow for reproducibility.

**Experimental Design of simulation procedures**

Overall, 3 different types of factors were varied that can be deducted from Table 1 and are detailed again in the simulation scripts provided.
Firstly, we varied the Sample Size in all studies, ranging from N = 50 to 100.000.
I included a smaller sample size N=50 for all studies, to be able to answer our substantive research questions in more detail.
Study 1b explicitly investigated the small sample bias of LSAM estimation in low sample sizes. 
Thus, only N=50 and N=100 are present in this study.
Additionally, the amount of misspecification was varied in all studies, either via different numbers of unmodelled residual correlations, cross-loadings, or both.
In Studies 1b and 4a, some population values for model parameters (phi, beta and/ or lambda) were varied, as well.
Besides studies 1 and 2, full factorial designs were implemented.
In Studies 1 and 2 I omitted conditions were both one positive and one negative value would be present.
I hypothesize that this was done in @robitzsch_comparing_2022 to avoid cancellation of biases, but the author does not give reasoning for this decision himself.
Studies 4 and 4a looked at the differential performance of the estimators in a model that included a non-saturated structural model (i.e. regressions between some of the factors).
These studies were replications not only of the paper by @robitzsch_comparing_2022, but of the first paper on the SAM approach by @rosseel_structural_2022.
I extended them to investigate the interaction of beta and N for the 5-factor regression model, as this again was of interest four our substantial research questions.

**Method Selection**

In terms of estimation methods, I used constrained maximum likelihood and unweighted least squares estimation, so that loadings and variance parameters were given the constraints that they had to be positive and larger than 0.01.
These were implemented in  classical SEM-estimation, as well as both in their LSAM and GSAM variants.
Exceptions were studies 1b, 4 and 4a, where only LSAM was investigated, as results did not really differ between the two different SAM-methods.

**Performance Measures**

I calculated the bias and RMSE of the estimated factor correlations in all studies, as well as the standard deviation of the one factor correlation present in Studies 1,2 and 3.
For the type of bias calculated, I oriented on @robitzsch_comparing_2022, besides in Study 1b.
Thus, I calculated average relative bias in Studies 1, 2 and 3, and average absolute bias in Studies 1b, 4 and 4a.
In Study 1b, I took the absolute value to see if negative and positive biases canceled each other out in the original study for conditions with lower phi values.
In Addition to what was done in @robitzsch_comparing_2022, I calculated confidence intervals for the bias estimates, but omitted them in the results tables for presentation purposes.
The exact computation of the performance measures is detailed in the simulation scripts and results.pdf file in my sub-folder of the github repository.

I did not include a detailed mechanism to capture model convergence as detailed in the first substantive research question.
As @robitzsch_comparing_2022 argue in their paper, and was showed already in other simulations, using constrained maximum likelihood estimation should resolve convergence issues of classical maximum likelihood estimation in smaller samples.
I did include, however, a mechanism to track the total number of warnings for each estimation and compare it to the total number of estimation as a sanity check.

For interpretation of results, I oriented on cut-offs that were used in the original paper by @robitzsch_comparing_2022.
For Bias, I interpreted difference of 0.05 or higher as substantial.
For SD, I explicitly mentioned percentage reductions of more or equal to 5%.
For RMSE, the same interpretation was used for differences of 0.03 or higher. 
The full result analysis is available here: <https://github.com/lkosanke/AdversarialSimulation/blob/main/LK/results.pdf>.
The same folder contains all simulation scripts that were used.
The simulation was repeated 1500 times for each Study.

**Software**

All analyses were conducted in R.
I used the packages lavaan, purrr, tidyverse, furrr to conduct the simulations, as well as knitr and kableExtra for presenting the results.











\newpage
# Bibliography